Decision Support and Health Insurance Choice

### 2021-03-17 finals/Paper.tex
Update decision assistance portion of code, remove Julia estimation from my end

Our overarching goal is to estimate the effect of decision assistance on health insurance decisions; however, there are perhaps many ways of measuring ``health insurance decisions''. One approach is to estimate demand for health insurance in a traditional discrete choice framework. This would allow us to quantify individuals' willingness to pay for decision assistance as well as the effect of decision assistance on choice probabilities. Another approach is to focus specifically on ``dominated choices'', which are relatively clearly defined and observable in our empirical context. This latter approach lacks the richness of the discrete choice demand framework but benefits from a focus on a specific outcome of obvious policy and welfare relevance. We consider both approaches in our analysis, as detailed in the remainder of this section.

>>>>

Our overarching goal is to estimate the effect of decision assistance on health insurance decisions; however, there are many ways of measuring ``health insurance decisions''. One approach is to estimate demand for health insurance in a traditional discrete choice framework. This would allow us to quantify individuals' willingness to pay for decision assistance as well as the effect of decision assistance on choice probabilities. Another approach is to focus specifically on ``dominated choices'', which are relatively clearly defined and observable in our empirical context. This latter approach lacks the richness of the discrete choice demand framework but benefits from a focus on a specific outcome of obvious policy and welfare relevance. We consider both approaches in our analysis, as detailed in the remainder of this section.

### 2021-03-17 finals/_Abstract_ASHEcon_201910.tex
Update decision assistance portion of code, remove Julia estimation from my end

We have data on 6,401,473 enrollee/year observations from the California
health insurance exhanges from 2014 to 2017. Our data include a variety
of individual and household characteristics, plan choices and plan
characteristics, and information on the type of decision assistance used
by the enrollee (if any). From these data, we can identify each
household's set of possible health insurance plans, and we employ
premium and cost sharing subsidy formulas to calculate health insurance
costs for each possible plan for each household.

@@

We first estimate overall demand for health insurance using a nested
logit discrete choice model, as in Saltzman (2019). We then identify
specific instances in which the observed plan choice is dominated by
some other plan in an individual's choice set. For example, Gold and
Platinum tier plans are dominated for any household that is eligible for
cost-sharing subsidies and with incomes below 150\% of the federal
poverty level. We estimate the effect of decision assistance on
dominated choices with a linear probability model, allowing for year and
household fixed effects.

@@

Our nested logit models establish strong evidence that decision
assistance matters for insurance choice. Turning specifically to
dominated choices, our baseline results suggest that individuals with
decision assistance are 0.37 percentage points less likely to make a
dominated choice. On a base of 1.9\%, this reflects a 20\% decrease in
the probability of making a dominated choice.

We also find strong heterogeneities in the effects of different forms of
decision assistance. In particular, we find that individuals using
publicly provided decision assistance are 0.43 percentage points less
likely to select a dominated plan, while individuals using a private
insurance agent are 0.16 percentage points less likely to select a
dominated plan.

>>>>

Our final dataset consists of 3,200,080 household/year observations from
the California health insurance exhanges from 2014 to 2019. Our data
include a variety of household characteristics, plan choices and plan
characteristics, and information on the type of decision assistance used
by the enrollee (if any). From these data, we can identify each
household's set of possible health insurance plans, and we employ
premium and cost sharing subsidy formulas to calculate health insurance
costs for each possible plan for each household.

@@

We first estimate overall demand for health insurance using a nested
logit discrete choice model, as in Saltzman (2019). We then identify
specific instances in which the observed plan choice is dominated by
some other plan in an individual's choice set. For example, Gold and
Platinum tier plans are dominated for any household that is eligible for
cost-sharing subsidies and with incomes below 150\% of the federal
poverty level. We estimate the effect of decision assistance on
dominated choices with a linear probability model, allowing for year,
insurer, and region fixed effects.

@@

Our nested logit models establish strong evidence that decision
assistance matters for insurance choice. Turning specifically to
dominated choices, our baseline results suggest that individuals with
decision assistance are 1.16 percentage points less likely to make a
dominated choice. On a base of 2.8\%, this reflects a 41\% decrease in
the probability of making a dominated choice.

We also find evidence fo heterogeneities in the effects of different
forms of decision assistance. In particular, we find that individuals
using publicly provided decision assistance are 0.91 percentage points
less likely to select a dominated plan, while individuals using a
private insurance agent are 1.26 percentage points less likely to select
a dominated plan.
